Lefse on gene orthologs

### 2019-10-18 scripts/10_barplot_genefamilies.Rmd
update

```{r}

>>>>

```{r}
# load the lefse res of tox
# the input : lefse res files
fns <- list.files('../data/lefse_genefam/', pattern = 'genefam_abundace_pheno__[CR|Toxicity].+res$', full.names = T)
fns_name <- list.files('../data/lefse_genefam/', pattern = 'genefam_abundace_pheno__[CR|Toxicity].+res$')

# join all of the tables feature together
feature <- fns %>% 
  set_names(fns_name) %>% 
  # when meeting parsing failures, you need to specify all column types.
  map(~ read_tsv(., col_names = c('genefam','xx','direction','score','pval'),  col_types = 'ccccc') %>% 
        filter(!is.na(score))) %>% 
  bind_rows(.id = 'group') %>% 
  mutate(group = str_replace(group, 'genefam_abundace_pheno__','')) %>% 
  mutate(group = str_replace(group, '.res$','')) %>% 
  select(-xx, -pval)

# change the "N" direction to be minus score
# feature <- bind_rows(
#   feature %>% 
#     split(.$direction) %>% 
#     pluck('N') %>% 
#     mutate(score = -score),
#   feature %>% 
#     split(.$direction) %>% 
#     pluck('Y') 
# ) %>% 
#   arrange(group, pathway, score)

feature %>% 
  write_csv('../data/lefse_genefam/with_unmapped_sig_feature.csv')

### 2019-10-18 scripts/11_lefse_geneorthologs.Rmd
update

```{r}
stra_go <- read_tsv('../data/humann2_res/genefamily_split_KO/humann2_genefamilies_KO_regroup_relab_stratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance-RPKs$','')))

@@

```{bash}
bash cat_combi_genef.sh
bash format_input_genef.sh
bash run_lefse_genef.sh
bash plotting_de_feature_genef.sh
```

>>>>

```{r}
stra_go <- read_tsv('../data/humann2_res/genefamily_split_KO/humann2_genefamilies_KO_regroup_relab_stratified.tsv') %>% 
  rename(sampleid = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance-RPKs$',''))) %>% 
  # remove the ungrouped since it's not really giving gene fam info
  filter(! str_detect(sampleid, '^UNGROUPED'))

@@

```{bash}
bash cat_combi_genef.sh
bash format_input_genef.sh
bash run_lefse_genef.sh
